%-------------------------
% Resume in Latex
% Author : Sabin Maharjan
%------------------------

\input{glyphtounicode}
\pdfgentounicode=1

\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage{tabularx}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Sabin Maharjan}}\\
	sabinmhx@gmail.com $\cdot$ https://sabin-maharjan.com.np $\cdot$ https://linkedin.com/in/sabinmhj/\\
\end{center}



%==== Experience ====%
\header{Education}
\vspace{1mm}

\textbf{Tribhuvan University} \hfill Kathmandu, NP\\
\textit{Bachelor of Science; Major: Computer Science; Grade: Distinction} \hfill Nov 2019 - Nov 2023\\
\vspace{-1mm}
\

\textbf{National School of Sciences} \hfill Kathmandu, NP\\
\textit{High School Diploma; Major: Biology \& Mathematics; Grade: A} \hfill Jul 2017 - Aug 2019\\
\vspace{-1mm}
\

\textbf{National United School} \hfill Kathmandu, NP\\
\textit{Secondary School; Major: Computer Science \& Mathematics; Grade: A+} \hfill Jan 2007 - Jun 2017\\
\vspace{-1mm}
\


%==== Skills ====%
\header{Skills}
\begin{tabularx}{\textwidth}{ l X } 
	Programming Languages: & Java, Python, Dart, Kotlin, C\#      \\
	Libraries \& Frameworks:  & Spring Boot, Flutter, Django, .NET  \\
    Databases:  & MySQL, PostgreSQL, MS SQL, Oracle SQL  \\
    Tools \& Platforms:  & Git, Docker, Firebase, Netlify, Vercel \& Jira \\
\end{tabularx}
\vspace{2mm}

%==== Projects ====%
\header{Projects}

{\textbf{Bharnaa}}\hfill https://github.com/sabinmhx/bharnaa\\
\textit{Online Medical Appointment System in Java}
\begin{itemize} \itemsep 1pt
	\item Proficiently utilized Java Spring Boot, Spring Data JPA, Spring Security, Hibernate, PostgreSQL.
    \item Implemented secure user authentication and HIPAA-compliant data protection.
    \item Executed over 150 test cases, resulting in a 98 \% defect identification rate.
\end{itemize}
\vspace*{2mm}

{\textbf{Sortify}}\hfill https://github.com/sabinmhx/sortify\\
\textit{Sorting Algorithm Visualizer in Java}
\begin{itemize} \itemsep 1pt
	\item Integrated multiple sorting algorithms, including Bubble Sort, Insertion Sort, Selection Sort, Merge Sort, Shell Sort, and Quick Sort.
	\item Added user controls to adjust the speed of the visualization, enabling users to observe the sorting process at different rates.
\end{itemize}
\vspace*{2mm}

{\textbf{Attendance}}\hfill https://github.com/sabinmhx/attendance\\
\textit{Attendance System with Face Recognition in Python}
\begin{itemize} \itemsep 1pt
	\item Developed a Python-based attendance system to streamline the process of tracking student attendance in college classes.
	\item Utilized OpenCV's deep learning-based face detection model, achieving an impressive 95\% accuracy rate in detecting student faces.
    \item Implemented Haar Cascade classifiers to detect specific facial features, such as eyes and mouths, enhancing the accuracy of face detection even in challenging scenarios.
\end{itemize}
\vspace*{2mm}

{\textbf{KitabPremi}}\hfill https://github.com/sabinmhx/kitabpremi\\
\textit{Online Bookstore Website in PHP}
\begin{itemize} \itemsep 1pt
	\item Built an e-commerce web project for buying and selling books using HTML, CSS, JS, PHP and MySQL.  
	\item Integrated payment gateway with Paypal Sandbox using Paypal API.
    \item Incorporated the DomPDF library allowing administrators to generate professional invoices for book orders.
\end{itemize}
\vspace*{2mm}

%==== Awards ====%
\header{Awards}
{Mahatma Gandhi Scholarship for High School} \hfill 2017\\
\vspace*{2mm}
{NIST Principal Scholarship for High School} \hfill 2017\\
\vspace*{2mm}

\ 
\end{document}
